Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-11 prop_letter.tex
After meeting...

\keywords{Finite precision measurement, the Born rule, Gleason's
theorem, the Kochen-Specker theorem, interval-valued probability measure,
discrete quantum theory}

@@

In this paper, we extend our previous work on the foundations of
computability in quantum mechanics by exploring the application of
interval-valued probability measures (IVPM) to achieving a coherent
formulation of finite-resource quantum mechanics.  In particular, we quantify the concept of imperfect quantum measurement and its impact on the interpretation of the Kochen-Specker and Gleason theorems and their implications for the foundations of quantum mechanics.

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality\nb\cite{BarrettKent2004,Appleby_2005}.  For example,
Meyer\nb\cite{PhysRevLett.83.3751} and Mermin\nb\cite{Mermin1999} disagree
on whether finite-precision measurements invalidate the Kochen-Specker
theorem\nb\cite{kochenspecker1967,peres1995quantum}. In particular,
the Kochen-Specker theorem is based on the two sphere\nb$S^{2}$
cannot be colored by red and green such that any orthogonal basis
has exactly one red vector. On the one hand, Meyer argued that the
rational dense subset of $S^{2}$, $S^{2}\cap\mathbb{Q}^{3}$, is
colorable, and we cannot distinguish $S^{2}$ and $S^{2}\cap\mathbb{Q}^{3}$
since finite precision measurement\nb\citep{PhysRevLett.83.3751,Szangolies2015}.
On the another hand, Mermin argued any physical outcome must be a
continuous function on the experimental configuration so that small
experimental imperfection should not ``nullify'' an idealized theorem\nb\citep{Mermin1999,Szangolies2015}.
Discussion
has continued on whether contextuality is consistent with  experimental outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
fundamental question is how to make mathematical theories of quantum mechanics that are intrinsically, rather than only implicitly, consistent with the resources available for the realistic accuracy of an actual measurement.

>>>>

\begin{comment}
\keywords{Finite precision measurement, the Born rule, Gleason's
theorem, the Kochen-Specker theorem, interval-valued probability measure,
discrete quantum theory}
\end{comment}

@@

In this paper, we extend our previous work on the foundations of
computability in quantum physics by exploring the application of
interval-valued probability measures (IVPM) to achieving a coherent
formulation of finite-resource quantum mechanics.  In particular, we quantify the concept of imperfect quantum measurement and its impact on the interpretation of the Kochen-Specker and Gleason theorems and their implications for the foundations of quantum mechanics.

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality\nb\cite{BarrettKent2004,Appleby_2005}, which refers to the fact that the results of measuring compatible sets of observables depend  on whether they are measured together or separately.  For example,
Meyer\nb\cite{PhysRevLett.83.3751} and Mermin\nb\cite{Mermin1999} disagree
on whether finite-precision measurements invalidate the spirit of the Kochen-Specker
theorem\nb\cite{kochenspecker1967,peres1995quantum}, which is a mathematical statement about contextuality.   The Kochen-Specker theorem asserts that, in a Hilbert space of dimension
$d \ge 3$, it is impossible to associate definite measured values, $\mu(P_i)= 0$
or $1$, with every projection operator\nb$P_i$, in such a way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then $\sum_i \mu(P_i) = 1$. In contrast, Meyer showed that 
one {\it can\/}  assign definite values $0$ or $1$ to the measurement outcome $\mu(P_i)$ when the Hilbert space is defined over the field of rational numbers, therefore nullifying the theorem\nb\citep{PhysRevLett.83.3751}.
However, Mermin then argued that measurement outcomes must depend smoothly
on slight changes in the experimental configuration. Mermin therefore claimed that 
the impact of Meyer's negative result  is ``unsupportable''\nb\citep{Mermin1999}. 
Discussion
has continued on whether contextuality is consistent with  experimental outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
A fundamental question is how to address this controversy by developing
 mathematical theories of quantum mechanics that are intrinsically, rather than only implicitly, consistent with the resources available for the realistic accuracy of an actual measurement.
